Flatiron cleaning

### 2022-05-26 Rmd/Manuscript rdi analysis.Rmd
Add practice type analysis

```{r library, include=FALSE}
library(tidyverse)
library(data.table)
library(lubridate)
library(psych)
library(ggplot2)
library(gtsummary)
library(survminer)
library(survival)
library(mice)
```

```{r loadd}
creatinine <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/creatinine.rds")
weight <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/weight.rds")
height <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/height.rds")
body_surface_area <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/body_surface_area.rds")
areaUC <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/areaUC.rds")
clinical_data <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/clinical_data.rds")
Treatment <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/Treatment.rds")
```

@@

study_consort %>%
  ggplot() + 
  geom_consort() +
  theme_consort(margin_h = c(1,6), margin_v = c(0,30))
```
<br>

>>>>

```{r library, include=FALSE}
library(tidyverse)
library(here)
library(data.table)
library(lubridate)
library(psych)
library(ggplot2)
library(gtsummary)
library(survminer)
library(survival)
library(mice)
```

```{r loadd}
creatinine <- read_rds(paste0(here(), "/creatinine.rds"))
weight <- read_rds(paste0(here(), "/weight.rds"))
height <- read_rds(paste0(here(), "/height.rds"))
body_surface_area <- read_rds(paste0(here(), "/body_surface_area.rds"))
areaUC <- read_rds(paste0(here(), "/areaUC.rds"))
clinical_data <- read_rds(paste0(here(), "/clinical_data.rds"))
Treatment <- read_rds(paste0(here(), "/Treatment.rds"))
practice <- read_rds(paste0(here(), "/practice.rds"))
```

@@

study_consort %>%
  ggplot() + 
  geom_consort() +
  theme_consort(margin_h = c(1,6), margin_v = c(0,30))
```
<br>
```{r}
practice %>% 
  # Limit to the patietns after exclusion criteria
  filter(str_detect(PatientID, paste(Frontline$patientid, collapse = "|"))) %>% 
  select(PracticeType) %>%
  tbl_summary()
```
<br>
